

## FISHFREAKS

Analyse cell proportions in 2x2 contingency tables, get results out easily with jagstools, plot.

### If necessary install ```jagstools```
```{r jagstools, eval=FALSE}
install.packages('devtools')
library("devtools")
install_github(repo='jagstools', username='johnbaums')

```


Get your packages on.

```{r}
library("jagstools")
library("R2jags")
library("ggplot2")
```


### Fish-eating Freaks
Is it true that cat lovers become like cats and eat heaps of fish?

Only a Bayesian 2x2 contingency table analysis could possibly dispel this vile besmirchery.

Interview question one: *"Do you like dogs or cats better?"*

Answers must be either *"cat"* or *"dog"*.

Interview question two: *"Do you eat fish?"*

Answers must be either *"yes"* or *"no"*.

There are 24 respondents.

Data are:
```{r data}
contdat1 <- c("dog", "cat", "dog", "dog", "cat", "cat", "dog", "cat", "dog", "dog", "cat", "cat", "dog", "cat", "dog", "dog", "cat", "cat", "dog", "cat", "dog", "dog", "cat", "cat")

contdat2 <- c("yes", "yes", "no", "no", "yes", "yes", "no", "yes", "no", "no", "yes", "yes", "yes", "yes", "no", "no", "yes", "yes", "no", "yes", "no", "no", "yes", "yes")
```

So 


Our model looks like:
```{r}
cat('
    model{
    for (i in 1:j) {
    log(p[i]) <- k1[A[i]] + k2[B[i]] + k12[A[i], B[i]]
    }
    
    pp <- sum(p[1:j])
    
    for (i in 1:j) {
    pr[i] <- p[i]/pp
    }
    
    odds_2 <- pr[4]/pr[3]
    odds_1 <- pr[2]/pr[1]
    odds_ratio <- odds_2 / odds_1
    
    d[1:j] ~ dmulti(pr[], N)  
    
    k1[1] <- 0 #  reference condition
    k2[1] <- 0   
    k12[1, 1] <- 0
    k12[1, 2] <- 0
    k12[2, 1] <- 0
    
    k1[2] ~ dnorm(0, 0.000001)
    k2[2] ~ dnorm(0, 0.000001)
    k12[2, 2] ~ dnorm(0, 0.000001)
        
    
    }
    
    ',file=(model.cont<-tempfile()))
```
Why? Look at Mick's book is why. No more questions.


To input our data ino the model we do this
```{r mung data}
contdat <- list(contdat1, contdat2)
dat <-table(contdat)
  
j <- 4 #number of elements in 2x2 contingency table
N <- sum(dat) # number of samples
d <- c(dat)
A <- c(1, 1, 2, 2) # categories in contingency table
B <- c(1, 2, 1, 2) # categories in contingency table
```


JAGS need more stuff
```{r jags stuff}
jags.data <- list(j = j, N = N, d = d, A = A, B = B)

jags.inits <- NULL
  
jags.params <- c("odds_ratio", "k1", "k2", "k12", "pr")

n.burnin <- 10000

n.iter <- 50000

n.thin <- 1

n.chains <- 3
```

Now call our model with R2jags
```{r call}
catfish <- jags(data = jags.data,
                inits = jags.inits,
                parameters.to.save = jags.params,
                model.file = model.cont,
                n.chains = n.chains,
                n.iter = n.iter,
                n.burnin = n.burnin,
                n.thin = n.thin)
```

We can look at our JAGS model output now
```{r}
catfish
```

Hmmm, looks fishy. What is that wierd object anyway? Don't be koi about it.
```{r}
class(catfish)
```

`rjags` what the smoking salmon does that mean?
```{r}
is.list(catfish)
```

List? Booooring

```{r}
str(catfish)
```
Ewwwww. Yuk.

I want my results in useable format!

```{r}
catfish$BUGSoutput$mean$pr
```

Ur list sux mister R2jags. 


But no need to reinvent the whale.

Yay `jagstools`

Let's get those precious precious data out of the nasty list

```{r}
odds <- jagsresults(catfish, params = c("odds_ratio"))

pr <- jagsresults(catfish, params = c( "pr"))
```

```{r}
odds

pr
```

Wow even a goldfish could do that! It looks much better.

Now I want to plot them to see if those cat people really are *fishy freaks*

And not all those data, just the mean and 95% credible interval.

```{r}
fishypr <- pr[, c('mean', "2.5%", "97.5%")]
colnames(fishypr)[2] <- 'CIlower'
colnames(fishypr)[3] <- 'CIupper'
fishypr <- as.data.frame(fishypr)
```


Ooh look here's a function I already had to do that.
```{r}
cplot <- function (cpdat, q = c("Normal", "Normal", "Fisheater", "Fisheater"), ws = c("Cat freak", "Dog lover", "Cat freak", "Dog lover")){
  plotdata <- as.data.frame(cbind(q, ws, cpdat))
  
  ggplot(plotdata, aes(x = ws, y = mean)) + geom_bar(width = 0.75, stat = 'identity', aes(x = ws, fill = ws), colour = "grey") + facet_grid(. ~ q) + scale_fill_manual(values = c("red", "yellow"), guide = 'none') + labs(x = NULL, y = NULL) + geom_errorbar(position = "dodge", width = 0.25, aes(ymin = CIlower, ymax = CIupper))
}

```



```{r}
cplot(fishypr)
```

##Oh.

##My.

##Cod.
